The History of Social Work Research: A Data Science Perspective

### 2015-02-03 Analysis.Rmd
Minor updates.
Processed R datafiles as standalone objects.

# Wrangle the data with the BWR function suite
ebscoBWR.f(csv=FALSE, path=path)
#save(bwr.df, file = "HistoricalArticles.R")
```

@@

bwr.df$record <- ifelse(bwr.df$record == "The Family", 
                       "Families in Society",
                       ifelse(bwr.df$record == "Journal of Social Casework",
                       "Families in Society",
                       ifelse(bwr.df$record == "Social Casework",
                       "Families in Society",
                        bwr.df$record)))

bwr.df$record <- ifelse(bwr.df$record == "Social Work in Education", 
                       "Children & Schools", 
                        bwr.df$record)

>>>>

# Wrangle the data with the BWR function suite
ebscoBWR.f(csv=FALSE, path=path, psycInfoOnly = FALSE)
save(bwr.df, file = "fullDF.R")
```

@@
